2013 flood edits

### 2024-06-28 sept2013_edits.Rmd
kge and pbias by year

library(tidyverse)
library(plotly)
library(lubridate)
library(knitr)
library(kableExtra)
library(hydroGOF)
library(here)

@@

@@

>>>>

library(tidyverse)
library(plotly)
library(lubridate)
library(knitr)
library(kableExtra)
library(hydroGOF)
library(here)
library(viridis)

@@

## Q KGE by year

flow_year <- flow %>%
  drop_na() %>%
  mutate(year = year(date)) %>%
  group_by(year) %>%
  summarize(grid_allNA = KGE(grid_allNA, obs),
            grid_all25 = KGE(grid_all25, obs),
            gridall = KGE(grid_all, obs),
            statn_all25 = KGE(statn_all25, obs),
            statn_allNA = KGE(statn_allNA, obs),
            statnall = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

flow_kge <- flow_year %>%
  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
  pivot_wider(names_from = 'year', values_from = 'kge')

flow_kge %>%
  kable(.) %>%
  kable_styling()

data_long <- pivot_longer(flow_kge, cols = -model_run, names_to = "year", values_to = "kge")

ggplot(data_long, aes(x = model_run, y = year, fill = kge)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(option = "viridis", name = "KGE", direction = -1) +
  geom_text(aes(label = round(kge, 2)), color = "grey", size = 4) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Year")

@@

## Pbias by year

flow_year <- flow %>%
  drop_na() %>%
  mutate(year = year(date)) %>%
  group_by(year) %>%
  summarize(grid_allNA = pbias(grid_allNA, obs),
            grid_all25 = pbias(grid_all25, obs),
            gridall = pbias(grid_all, obs),
            statn_all25 = pbias(statn_all25, obs),
            statn_allNA = pbias(statn_allNA, obs),
            statnall = pbias(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

flow_pbias <- flow_year %>%
  pivot_longer(!year, names_to = 'model_run', values_to = 'pbias') %>%
  pivot_wider(names_from = 'year', values_from = 'pbias')

flow_pbias %>%
  kable(.) %>%
  kable_styling()

data_long <- pivot_longer(flow_pbias, cols = -model_run, names_to = "year", values_to = "Pbias")

ggplot(data_long, aes(x = model_run, y = year, fill = Pbias)) +
  geom_tile(color = "white") +
 scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0, name = "Pbias") +
  geom_text(aes(label = round(Pbias, 2)), color = "black", size = 4) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Year")
